A Large-Scale Study of the Use of Eval in R

### 2020-08-22 inst/paper/main.tex
intro

While there has been previous work investigating the usage of \eval in web
programming and JavaScript, there are no other studies that shed light on
the usage of \eval in other programming languages and application domains.
It is thus reasonable to wonder if the results from previous work can be
carried over to other contexts. For this paper, we have picked the data
science language R~\cite{r} as our object of study. R is both different from
JavaScript in linguistic terms and in terms of its user base. JavaScript was
designed to run untrusted code in browser, while R was design for
statistical computing on a desktop. JavaScript is used as a general purpose
language by a wide community of programmers; while R is used for scientific
computing by data scientist and domain experts with, often, limited
programming experience.

This paper sets out to highlight the differences in usage patterns between
these two languages and user communities. Our results are broadly applicable
as they increase our understanding of the range of uses of \eval, present
new patterns, and hopefully provide insights into reasonable
under-approximations of \eval. More narrowly, for researchers interested in
static analysis of data science code, we provide a publicly available corpus
of programs and a toolchain that can be customized to deliver different
types of information about the behavior of \eval.

While the worst case is indeed pretty bad, previous work has found that
in many cases eval can be fairly inoccuous or at least much less dangerous
that the worst case.

There has been research in understanding the behavior of eval in the context
of web programming and in particular the JavaScript language.

>>>>

While there has been previous work investigating the usage of \eval in web
programming and JavaScript~\cite{ecoop11}, there are no other studies that
shed light on the usage of \eval in other programming languages and
application domains.  It is thus reasonable to wonder if the results from
previous work can be carried over to other contexts. For this paper, we have
picked the data science language R~\cite{r} as our object of study. R is
both different from JavaScript in linguistic terms and in terms of its user
base. JavaScript was designed to run untrusted code in browser, while R was
design for statistical computing on a desktop. JavaScript is used as a
general purpose language by a wide community of programmers; while R is used
for scientific computing by data scientist and domain experts with, often,
limited programming experience.

This paper sets out to highlight the differences in usage patterns of \eval
between these two languages and user communities. Our results are broadly
applicable as they increase our understanding of the range of uses of \eval,
present new use-cases, and, hopefully, provide insights into reasonable
under-approximations. More narrowly, for researchers interested in static
analysis of data science code, we provide a publicly available corpus of
programs and a toolchain that can be customized to deliver fine-grained
information about the usage and impact of \eval.

Our methodology for this work bows to the fact that static analysis of R is
difficult, instead we focus on dynamic analysis. To observe \eval we have
built a two-level monitoring infrastructure: we are able to monitor R
programs by instrumentation -- this gives us access to many user-visible
properties of R programs -- and we also can monitor the inner working of the
R interpreter -- this allows us to capture details of execution that are not
exposed at the source level.

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above, R is a lazy language, like Haskell, the authors have informally
  surveyed end-users, some of them computer scientists, and did not find a
  single one aware of that fact. Library developers, on the other hand, tend
  to know about laziness and program defensively around it.} Thus, our
corpus distinguished between ,....
